Supplementary Content

### 2022-02-22 experiments/2_supplement/supplement.Rmd
#22 `2_supplement`

```{r repl_meth1, echo=FALSE, eval = TRUE}
repl_meth <- readRDS(here("experiments/0_ss_finding/replication_method/data/ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
temp_meth <- readRDS(here("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
```

@@

```{r div-temp-eventdef1, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method_eventdef1.RDS"))

@@

```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("experiments/0_ss_finding/replication_method/processed_data/stab_data_replication_method.RDS"))

@@

```{r div-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth1)', fig.height=7, fig.width=6, fig.align="center"}
all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))

@@

```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=8, fig.width=8, fig.align="center"}
single_1e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_1e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_1e6
fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
```

@@

```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=8, fig.width=8, fig.align="center"}
single_2e6 <- readRDS(here("experiments/0_ss_finding/temporal_method/data/single_2e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_2e6
fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
```

@@

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here(paste0("experiments/0_ss_finding/temporal_method/data/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

@@

```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))

>>>>

```{r repl_meth1, echo=FALSE, eval = TRUE}
repl_meth <- readRDS(here("data/0_ss_finding/replication_method/ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
temp_meth <- readRDS(here("data/0_ss_finding/temporal_method/ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
```

@@

```{r div-temp-eventdef1, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method_eventdef1.RDS"))

@@

```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data/0_ss_finding/replication_method/processed_data/stab_data_replication_method.RDS"))

@@

```{r div-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth1)', fig.height=7, fig.width=6, fig.align="center"}
all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))

@@

```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=8, fig.width=8, fig.align="center"}
single_1e6 <- readRDS(here("data/0_ss_finding/temporal_method/single_1e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_1e6
fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
```

@@

```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=8, fig.width=8, fig.align="center"}
single_2e6 <- readRDS(here("data/0_ss_finding/temporal_method/single_2e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_2e6
fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
```

@@

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here(paste0("data/0_ss_finding/temporal_method/ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here(paste0("data/0_ss_finding/temporal_method/stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

@@

```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))
